### 2014-08-18 analysis/network_properties.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

@@

```{r results='asis',echo=FALSE}
source("../R/experiment_utils.R")

#shows the k values explored and the number of networks
params <- read.exp.parameters("../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
params <- params[,c("cfg.id","num.networks","network.0.k")]

@@

require(stargazer)
stargazer(t(k_values), type="html", summary = FALSE)
stargazer(t(num_networks), type="html", summary = FALSE)

@@

We load the network data from the regular networks experiment with the `bigmemory` package which 
is more efficient in terms of memory management.
```{r message=FALSE}
source("../R/network.utils.R")
require(bigmemory)
network_data <- read.big.matrix(filename="../data/context_permeability/regular_networks/networks.csv", header=T, sep=";")
```

@@

par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 1")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")

@@

par(mfrow=c(1,1))
plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")
```

@@

require(stargazer)
stargazer(netprop.table, type="html", summary = FALSE)
```

@@

```{r}
#Collect the network data and create a data table to hold the network properties
require(parallel)

@@

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")

@@

require(ggplot2)

@@

@@

@@

@@

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Clustering Coefficient", x="Number of Networks")
plot 
```

@@

```{r}
#aggregate run data by k and networks
require(reshape2)

apl_data <- melt(props, id=c("k","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("k","networks","run"),measure.vars=c("clustering-coefficient"))

@@

#plot average path length for k = 1,2,3,4,5
net_props <- average_apl_data[average_apl_data$"k" <= 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

#plot for k = 10,20,30,40,50
net_props <- average_apl_data[average_apl_data$"k" >5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot

@@

#read the network data
require(bigmemory)
network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_networks/networks.csv", header=T, sep=";")

#Collect the network data and create a data table to hold the network properties
require(parallel)

@@

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(d_values)), label="network analysis")

@@

require(ggplot2)

@@

@@

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$d)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="D", y="Clustering Coefficient", x="Number of Networks")
plot 
```

@@

```{r}
#aggregate run data by k and networks
require(reshape2)

apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("d","networks","run"),measure.vars=c("clustering-coefficient"))

@@

#plot average path length for d = 1,2,3,4,5
net_props <- average_apl_data
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Average Path Length", x="Number of Networks")
plot

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Clustering Coefficient", x="Number of Networks")
plot

@@

>>>>

Load the dependencies for this report.
```{r}
source("../R/experiment_utils.R")
source("../R/network.utils.R")

library(stargazer)
library(reshape2)
library(ggplot2)

library(bigmemory)
library(parallel)
#to create a progress bar 
library(BBmisc)

@@

```{r results='asis',echo=FALSE}
#shows the k values explored and the number of networks
params <- read.exp.parameters("../data/context_permeability/regular_networks/param-space_2014-07-23_11:40:44experiment:0_.csv")
params <- params[,c("cfg.id","num.networks","network.0.k")]

@@

stargazer(t(k_values), type="html", summary = FALSE)
stargazer(t(num_networks), type="html", summary = FALSE)

@@

We load the network data from the regular networks experiment with the `bigmemory` package which 
is more efficient in terms of memory management.
```{r message=FALSE}
network_data <- read.big.matrix(filename="../data/context_permeability/regular_networks/networks.csv", header=T, sep=";")
```

@@

plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 1")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")

#print to pdf
pdf(paste("./pdf/","network_properties_merge_2_10regular.pdf"), width=15, height=5)
par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 1")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")
dev.off()

@@

#print to report
par(mfrow=c(1,1))
plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")

#print to pdf

pdf(paste("./pdf/","network_properties_1_20regular.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")
dev.off()

@@

stargazer(netprop.table, type="html", summary = FALSE)
```

@@

```{r}
#Collect the network data and create a data table to hold the network properties

@@

pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")

@@

#save this for later use
write.table(props, "../data/context_permeability/regular_networks/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE)

@@

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Average Path Length", x="Number of Networks")

#print to report
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

#print to pdf
pdf(paste("./pdf/","network_properties_apl_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

#print to pdf
pdf(paste("./pdf/","network_properties_cc_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

#print to pdf
pdf(paste("./pdf/","network_properties_cc_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()
```

@@

```{r}
#aggregate run data by k and networks
apl_data <- melt(props, id=c("k","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("k","networks","run"),measure.vars=c("clustering-coefficient"))

@@

#plot average path length for k = 1,2,3,4,5
net_props <- average_apl_data[average_apl_data$"k" <= 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_line_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

#plot for k = 10,20,30,40,50
net_props <- average_apl_data[average_apl_data$"k" >5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_line_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_line_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_line_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

#read the network data
network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_networks/networks.csv", header=T, sep=";")

#Collect the network data and create a data table to hold the network properties
## Number of workers (R processes) to use:
numWorkers <- 8

@@

pb <- makeProgressBar(min=0, max=(length(num_networks)*length(d_values)), label="network analysis")

@@

```{r}
props <- as.data.frame(props)
#save this for later use
write.table(props, "../data/context_permeability/scale-free_networks/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE)

@@

#print to pdf
pdf(paste("./pdf/","network_properties_apl_sf_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$d)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="D", y="Clustering Coefficient", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_sf_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()
```

@@

```{r}
#aggregate run data by k and networks
apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("d","networks","run"),measure.vars=c("clustering-coefficient"))

@@

#plot average path length for d = 1,2,3,4,5
net_props <- average_apl_data
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Average of Average Path Length", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_line_sf_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Average of Clustering Coefficient", x="Number of Networks")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_line_sf_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

@@

#Properties for Scale-free + Regular Configuration#

```{r}
#shows the d values explored and the number of networks
params <- read.exp.parameters("../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
params <- params[,c("cfg.id","network.0.k","network.1.d")]

#read the network data
network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_regular/networks.csv", header=T, sep=";")

#Collect the network data and create a data table to hold the network properties
## Number of workers (R processes) to use:
numWorkers <- 8

props <- NULL

k_values <- c(1:5,seq(10,50,10))
d_values <- c(1,2,3,4,5)

runs <- sort(unique(network_data[,"run"]))

pb <- makeProgressBar(min=0, max=(length(k_values)*length(d_values)), label="network analysis")

#pre-alocate a matrix for the network properties
props <- matrix(nrow=(length(k_values)*length(d_values)*length(runs)), ncol=7)
i <- 0

for(k in k_values){
  #reads the properties for all the k-regular networks with the given k and num_networks 
  for(d in d_values){
    cfg <- params[params$"network.0.k" == k & params$"network.1.d" == d,][[1]]

    props[(i+1):(i+100),] <- cbind(d,k,properties)
    i <- i + 100  
    #some progress feddback
    pb$inc(1,paste("reading k=",k,"d=",d,"\n"))
    gc()
  } 
}
pb$kill()

colnames(props)<-c("d","k","run","nodes","edges","clustering-coefficient","average-path-length")

props <- as.data.frame(props)

#save this for later use
write.table(props, "../data/context_permeability/scale-free_regular/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE, append=FALSE)

#props <- read.table("../data/context_permeability/scale-free_regular/network_properties.csv", sep = ",", header = T)

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Average Path Length", x="D")

#print to report
plot

pdf(paste("./pdf/","network_properties_apl_sf_kregular_12345.pdf"), width=7, height=5)
plot
dev.off()

net_props <- props[props$k >5,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Average Path Length", x="D")

#print to report
plot

pdf(paste("./pdf/","network_properties_apl_sf_kregular_1020304050.pdf"), width=7, height=5)
plot
dev.off()

Create box plots for clustering coefficient
```{r}
#create average path length box plots for k = 1,2,3,4,5
net_props <- props[props$k <= 5,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Clustering Coefficient", x="D")

#print to report
plot

pdf(paste("./pdf/","network_properties_cc_sf_kregular_12345.pdf"), width=7, height=5)
plot
dev.off()

net_props <- props[props$k >5,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Clustering Coefficient", x="D")

#print to report
plot

pdf(paste("./pdf/","network_properties_cc_sf_kregular_1020304050.pdf"), width=7, height=5)
plot
dev.off()

```{r}
#aggregate run data by k and networks
apl_data <- melt(props, id=c("k","d","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("k","d","run"),measure.vars=c("clustering-coefficient"))

average_apl_data <- dcast(apl_data, k + d ~ variable, mean)
average_clustering_data <- dcast(clustering_data, k + d ~ variable, mean)

#plot average path length for k = 1,2,3,4,5
net_props <- average_apl_data[average_apl_data$"k" <= 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="D")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_line_sf_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

net_props <- average_apl_data[average_apl_data$"k" > 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="D")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_apl_line_sf_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

```{r}
#plot average path length for k = 1,2,3,4,5
net_props <- average_clustering_data[average_clustering_data$"k" <= 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="D")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_line_sf_kreg_12345.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()

net_props <- average_clustering_data[average_clustering_data$"k" > 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="D")
plot

#print to pdf
pdf(paste("./pdf/","network_properties_cc_line_sf_kreg_1020304050.pdf"), width=7, height=5)
par(mfrow=c(1,1))
plot 
dev.off()
